%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[calibri]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{multicol}

% Set applicant's personal data for header
\name{Bernardo Ferrari}
\address{Florianópolis, Brazil \linebreak Milan, Italy}
\contacts{
	+55 48 99170-0004 \linebreak
	bernardo.mferrari@gmail.com \linebreak
	\url{https://tarberd.me/about}
}

\begin{document}

	% Print the header
	\makeheader{}

	\begin{cvsection}{About}
		\begin{cvsubsection}{}{}{}
		I am a Software Engineer with 5+ years of C++ experience and a Programming Language Researcher with 3+ years background on Refinement Types and LLVM front-end compiler implementation in Rust.
		\end{cvsubsection}
	\end{cvsection}

	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Engineer}{Cadence Design Systems}{May 2022 -- Present}
			Worked as part of the System-Level Verification IP team to enable PCIe SoC verification.
			\begin{itemize}
				\item Developed a simulator for the verification of the PCIe specification using modern \textbf{C++}.
				\item Developed \textbf{Python} \textbf{DevOps} applications to enable easier software development.
				\item Implemented learning practices on \textbf{TDD} and \textbf{C++} through coding dojos.
				\item Experience with remote work in a globally distributed team.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Compiler Researcher}{LASIGE}{Sep 2020 -- Present}
			Worked as part of the Software Quality research team with focus on programming languages.
			\begin{itemize}
				\item Designed a programming language formal \textbf{Type System} with \textbf{refinement types} called Ekitai.
				\item Developed an incremental \textbf{LLVM} front-end for Ekitai supporting the \textbf{C ABI} using \textbf{Rust}.
				\item Experience with remote work in a globally distributed team.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Undergrad. Teaching Assistant}{Federal University of Santa Catarina}{Jul 2019 -- Dec 2020}
			\begin{itemize}
				\item Courses: Compiler Construction; Formal Languages and Compilers; Computer Science Theory.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{EDA Researcher}{Embedded Computing Laboratory}{Jun 2016 -- Dec 2020}
			Worked as part of the EDA research team to build a modern \textbf{C++} library to enable EDA research and teaching.
			\begin{itemize}
				\item Developed cache-aware data structures and algorithms modern \textbf{C++} library for building EDA physical design applications. Developed parallel algorithms using \textbf{OpenMP}, \textbf{pThread} and \textbf{Boost}.
				\item Acted as Lead Software Engineer guiding the team in technical decisions regarding modern \textbf{C++} library Architecture and enforcing agile practices such as \textbf{TDD}, \textbf{Code Review}, \textbf{CI/CD}, and \textbf{KanBan}.
				\item Acted as Lead \textbf{DevOps} engineer developing the library build system in modern \textbf{CMake} and \textbf{Python}. Developed \textbf{CI/CD} pipelines for testing and distributing multiple \textbf{Linux} binary packages (e.g. rpm, deb, pacman, yocto).
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{CS Extension Program}{University of Santa Catarina}{Jul 2013 -- May 2014}
			Worked as part of the CS extension program group acting as \textbf{System Administrator}.
			\begin{itemize}
				\item Administrated the extension program \textbf{Linux} infrastructure and servers (e.g. \textbf{Linux Repositories}, \textbf{Web Services}, \textbf{SQL}, \textbf{Ldap}, \textbf{ArchLinux}, \textbf{Gentoo})
				\item Organized the Computer Science Week, a per semester event where multiple local companies would give talks and mini-courses to Undergraduate students.
				\item Aided Professors on teaching and research extension programs.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Ekitai} (2020 -- 2023). A programming language with refinement types using the \textbf{LLVM} ecosystem written in \textbf{Rust}.

				Project page: \url{https://github.com/tarberd/ekitai}

				\item \textbf{TongOS} (2003 -- 2004). A \textbf{Risc-V} multi-task multi-core Operational System written in \textbf{Rust}.

				Project page: \url{https://github.com/tong-os/tongOS}

				\item \textbf{Ophidian} (2016 -- 2019). A set of \textbf{Open-Source} high-performance \textbf{C++} libraries to assist the \textbf{Physical Design} step of \textbf{EDA} research and teaching.

				Project page: \url{https://gitlab.com/eclufsc/ophidian}.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\newpage
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Florianópolis, SC, Brazil}{Federal University of Santa Catarina}{2013 -- 2023}
			B.Sc.\ in Computing Science, GPA\@: 7.14/10.
			\begin{multicols}{2}
				\begin{itemize}
						\item Compiler Construction: 9.0/10
						\item Operational Systems II\@: 9.0/10
						\item Formal Languages and Compilers: 8.0/10
						\item Security: 8.0/10
						\item Data Structures: 8.0/10
						\item Computer Organization and Design: 7.5/10
				\end{itemize}
		  \end{multicols}
  	\end{cvsubsection}
		\begin{cvsubsection}{Cork, Ireland}{University College Cork}{2015 -- 2016}
			B.Sc.\ Exchange Program.
  	\end{cvsubsection}
	\end{cvsection}

	% \begin{cvsection}{Additional Experience and Awards}
	% 	\begin{cvsubsection}{}{}{}
	% 		\begin{itemize}
	% 			\item \textbf{Instructor (2003 – 2005):} Taught two full-credit Computer Science courses; average ratings of 4.8 out of 5.0.
	% 			\item \textbf{Third Prize, Senior Design Projects:} Awarded 3rd prize for Synchronized Calendar project, out of 100 projects.
	% 		\end{itemize}
	% 	\end{cvsubsection}
	% \end{cvsection}

	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item C++; C; Java; Objective-C; C\#.NET; SQL; JavaScript; XSLT; XML (XSD) Schema
				\item Visual Studio; Microsoft SQL Server; Eclipse; XCode; Interface Builder
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Natural Languages}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
					\item Portuguese (native)
					\item English (fluent)
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
\end{document}
